Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-14 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:14	23:16:40	(Fri14.Aug)

By definition, the beamformer output $z[n]$ can be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$. With static weights this would be referred to as the conventional delay-and-sum (DAS) beamformer. A large variety of weighting functions exists here for trading lateral resolution for improved noise suppression (contrast), but one always ends up with a compromise between the two~\cite{Harris1978}.

>>>>

A beamformer is a spatial filter we apply to backscattered wavefield data to estimate the scatter strength from a particular point or direction. A coarse adjustment is first obtained by applying delays to the sensor channels to negate the difference in travel time from the point of interest, thereby aligning the phase of the signals coming from that source. Next a set of weights, or window, is applied to the sensors to Finally a set of weights  , which in effect achieve this by applying delays and weigths to the sensor channels to coherently combine signals from the direction of interest.

Let the array be an $M$ element uniform linear array, 
By definition, the beamformer output $z[n]$ can be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$. With static weights this would be referred to as the conventional delay-and-sum (DAS) beamformer. A large variety of weighting functions exists here for trading lateral resolution for improved noise suppression (contrast), but one always ends up with a compromise between the two~\cite{Harris1978}.
